True versus apparent shapes of astrophysical bow shocks

### 2016-04-26 papers/Paper1/sec-application.tex
Use slightly higher N0 values
Reducing the HA98 values by factor of 2 was too extreme - changed it to
factor of 1.5 instead.  This means that we generally need lower
inclinations in order to match the ionizing flux
Fixed some typing errors.Enhanced conics scenario.

\begin{align}
\dot{M}_w &= \frac{\dot{M}_w^0}{2(k+1)}\left(1-\cos^{k+1}\theta\right) \label{eq:dotprop} \\
\mathrm{where} & M^0_w \equiv 4\piv_w r^2_{IF} n_0 \bar{m}\\
\dot{\Pi}_z &= \frac{v_w\dot{M}_w^0}{2(k+2)}\left(1-\cos^{5/2}\theta\right)  \label{eq:pir}\\
\dot{\Pi}_r &= \frac{1}{2}\dot{M}^0_w V_w I_k (\theta) \label{eq:piz}\\
I_k(\theta) & = \int^\theta_0 \cos^k \theta \sin^2\theta~d\theta
\dot{J}_w = 0 \label{eq:jdot}
\end{align}  
Combining equations  (\ref{eq:dotprop}) to (\ref{eq:jdot}) with equation (6) of \CRW{}  we can obtain the bow shock shape $R(\theta)$. Actually, we work with two different scenarios:
% as illustred in figure (\ref{fig:r-beta}), where we show the resulting bow shock shapes for two scenarios:
$k=1/2$ ak.a. the ``proplyd case'', following \citep{HA:1998}, and $k=0$, ak.a, the ``isotropic case'', following \CRW{}. The comparison betwwen both solutions is shown in figure (\ref{fig:r-beta}).

@@

Solving for $\theta_{1,90}$ from equation (\ref{eq:th190}) we find that:

@@

\begin{align}
B = \frac{\sqrt(\xi\beta)\left(1+\beta^{1/2}\right)}{(1-\xi\beta)\left(1+\frac{1}{5}\xi\beta\right)^{1/2}}
\label{eq:B}
\end{align}

@@

@@

Equations (\ref{eq:r90}),  (\ref{eq:Rcurv}) and (27) from \citep{Canto:1996} are labeled as ``analytic i=0'' in figure (\ref{fig:rad-beta}).

@@

Observationally, we can measure the projected radii. In order to estimate the model parameters is neccesary to measure at least two of the mentioned radii, being $R_0$ the
easiest to measure. Therefore, we may compare both $R_c$ and $R_{90}$ against $R_0$ as shown in figure (\ref{fig:prop-shell-rad}).

@@

Using equations (\ref{eq:Rcurv}) and (\ref{eq:B}) we can estimate the parameter of conic curves $\theta_c$ as a function of $(\beta,\xi)$. Continue edition from here...

>>>>

\begin{align}
\dot{M}_w &= \frac{\dot{M}_w^0}{2(k+1)}\left(1-\cos^{k+1}\theta\right) \label{eq:dotprop} \\
\mathrm{where} & M^0_w \equiv 4\pi v_w r^2_{IF} n_0 \bar{m}\\
\dot{\Pi}_z &= \frac{v_w\dot{M}_w^0}{2(k+2)}\left(1-\cos^{5/2}\theta\right)  \label{eq:pir}\\
\dot{\Pi}_r &= \frac{1}{2}\dot{M}^0_w V_w I_k (\theta) \label{eq:piz}\\
I_k(\theta) & = \int^\theta_0 \cos^k \theta \sin^2\theta~d\theta \\
\dot{J}_w = 0 \label{eq:jdot}
\end{align}  
Combining equations  (\ref{eq:dotprop}) to (\ref{eq:jdot}) with equation (6) of \CRW{}  we can obtain the bow shock shape $R(\theta)$. Actually, we work with two different scenarios:
% as illustred in figure (\ref{fig:r-beta}), where we show the resulting bow shock shapes for two scenarios:
$k=1/2$ ak.a. the ``proplyd case'', following \citep{HA:1998}, and $k=0$, ak.a, the ``isotropic case'', following \CRW{}. The comparison betwwen both solutions is shown in figure (\ref{fig:r-beta}).

@@

Solving for $\theta_{1,90}$ from equation (\ref{eq:th190}), using a small angle  approximation, we find that:

@@

\begin{align}
B = \frac{\sqrt(3\xi)\left(1+\beta^{1/2}\right)}{(1-\xi\beta)\left(1+\frac{1}{5}\xi\beta\right)^{1/2}}
\label{eq:B}
\end{align}

@@

This expansion is valid when k is integer or multiple of 1/2.

@@

--- Rethink if should be included on paper ---
Equations (\ref{eq:r90}),  (\ref{eq:Rcurv}) and (27) from \citep{Canto:1996} are labeled as ``analytic i=0'' in figure (\ref{fig:rad-beta}).

@@

--- Finished rethinking ---
Observationally, we can measure the projected radii. In order to estimate the model parameters is neccesary to measure at least two of the mentioned radii, being $R_0$ the
easiest to measure. Therefore, we may compare both $R_c$ and $R_{90}$ against $R_0$ as shown in figure (\ref{fig:prop-shell-rad}).

@@

Using equations (\ref{eq:Rcurv}) and (\ref{eq:B}) we can estimate the parameter of conic curves $\theta_c$ as a function of $(\beta,\xi)$ using equation (make it in conics section)

\begin{align}
\tan^2\theta_c &= 3\left| \frac{\xi\left(1+\beta^{1/2}\right)^2}{\left(1-\xi\beta\right)^2\left(1+\frac{1}{5}\xi\beta\right)}-\frac{1}{\left(1-\beta^{1/2}\right)}\right| 
\end{align}

With this we can use the results of section \ref{sec:conic} to estimate the projected conic shapes for bow shocks with different winds momenta and different density distributions. In figure () we show 
the theoretical conic curves for different vales of $\beta$ with a fixed $\xi$
